Type Refinements for the Working Class

### 2015-12-24 paper.tex
wording

Another seemingly paradoxical observation is also possible:

@@

At the very least, the fact that neither the naturals nor the atoms may be
embedded into the other commits us to a truly intuitionistic ontology, as
opposed to merely constructive one. In particular, our framework is
anti-classical in at least a na\"ive sense, because the Axiom of Choice puts
each set in bijection with a cardinal, whence it is impossible for neither of
two sets to embed in the other. However, it is important to note that as far as
the propositions-as-types principle is concerned, Computational Type Theory is
already anti-classical, as the undecidability of the halting program can be
observed internally.

>>>>

Another seemingly paradoxical observation is possible:

@@

At the very least, the fact that neither the naturals nor the atoms may be
embedded into the other commits us to a truly intuitionistic ontology, as
opposed to a merely constructive one. In particular, our framework is
anti-classical in at least a na\"ive sense, because the Axiom of Choice puts
each set in bijection with a cardinal, whence it is impossible for neither of
two sets to embed in the other. However, it is important to note that as far as
the propositions-as-types principle is concerned, Computational Type Theory is
already anti-classical, as the undecidability of the halting program can be
observed internally.
